\begin{bibliography}{}

\bibitem[Kuo and Sullivan(2001)]{1}
Kuo, E.F. and Sullivan W.C. 2001. Environment and Crime in the Inner City: Does Vegetation Reduce Crime? \textit{Environment and Behavior}. Vol 33, Issue 3, pp. 343 - 367.
\bibitem[Benefits of Urban Trees Guide(2016)]{2}
Benefits of Urban Trees Guide. A guide by Greenblue Urban. 2016. http://www.greenblue.com/wp-content/uploads/2016/05/Benefits-of-Urban-Trees.pdf 

\bibitem[Trees of Strength Project, NC-State]{3}
Trees of Strength Project, NC State Department of Horticultural Science https://projects.ncsu.edu/project/treesofstrength/benefits.htm

\bibitem[Kardan et. al.(2015)]{4}
Kardan, Omid and Gozdyra, Peter and Misic, Bratislav and Moola, Faisal and Palmer, Lyle J. and Paus, Tomáš and Berman, Marc G. 2015. Neighborhood greenspace and health in a large urban center. \textit{Scientific Reports}. 5, Article number: 11610 

\bibitem[Center for Public Impact(2016)]{5}
Center for Public Impact. Responding to climate change: Melbourne’s urban forest strategy. 2016.
 https://www.centreforpublicimpact.org/case-study/urban-forest/ 

\bibitem[Bureau of Meteorology and CSIRO(2016)]{6}
State of the Climate Report. 2016. Bureau of Meteorology and CSIRO. https://www.csiro.au/en/Showcase/state-of-the-climate 


\bibitem[City of Melbourne(2012)]{8}
URBAN FOREST STRATEGY: Making a great city greener 2012-2032, 2012, City of Melbourne
https://www.melbourne.vic.gov.au/SiteCollectionDocuments/urban-forest-strategy.pdf 

\bibitem[Morales(1980)]{9}
Morales, D.J. 1980. The contribution of trees to residential property value. \textit{Journal of Aboriculture} 6 (11): 305-308.
\bibitemp[Nowak et. al.(2014)]{10}
Nowak, D.J. Hirabayashi, S. Bodine, A. and Greenfield, E. 2014. Tree and forest effects on air quality and human health in the United States. \textit{Environmental Pollution}. 193. 119-129.
\bibitem[Anderson \& Cordell(1988)]{11}
Anderson, L.M.; Cordell, H.K. 1988. Influence of trees on residential property values in Athens, Georgia: a survey based on actual sales prices. Landscape and Urban Planning. 1988, 15: 1-2,153-164.
\bibitem[Yang et. al.(2016)]{12}
Yang, L. Qian, F. Song, D. and Zheng, K. 2016 Procedia Engineering Research on Urban Heat-Island Effect. \textit{Procedia Engineering}. 169. 11-18. 
\bibitem[Institute for Sustainable Futures, and University of Technology, Sydney(2014)]{13}
Benchmarking Australia’s Urban Tree Canopy: An i-Tree Assessment, Final report. 2014. Institute for Sustainable Futures, and University of Technology, Sydney.   http://202020vision.com.au/files/where_are_all_the_trees.pdf 

\bibitem[Urban Forest Strategy(2014)]{14}
URBAN FOREST STRATEGY: Making a great city greener 2012-2032, 2012, City of Melbourne http://melbourneurbanforestvisual.com.au/#mapexplore 

\bibitem[Encyclopedia Britannica(2014)]{15}
Plane Tree. Encyclopedia Britannica. March 19, 2014. Access Date: November 28, 2017.

\bibitem[Mount and Zumel(2016)]{16}
 Mount J and Zumel N (2016). vtreat: A Statistically Sound data.frame Processor/Conditioner. R package version 0.5.27, URL https://CRAN.R-project.org/package=vtreat. 



\end{bibliography}